---
title: "Beta_p estimations vs rq() coefficients on NMES1988"
output: pdf_document
---

```{r setup, include=FALSE}
rm(list=ls())
library(coda)
library(quantreg)
library(mcmcse)
library(knitr)

set.seed(0)
knitr::opts_knit$set(root.dir = "C:\\Users\\juyil\\Dropbox\\Study\\GitHub\\Bayesian-gibbs-sampler\\R")
library(AER)
data("NMES1988")

```

```{r}
response = NMES1988[,1]   # Number of physician office visits.
dat = NMES1988[c(8,11,15,16)] # Remove the responses

# Center and scale the continuous predictors:
# dat[c(2,4)]= scale(dat[c(2,4)])
```

```{r, echo=FALSE}
## Setup
itr_total = 1200
quantiles=c(0.1, 0.5, 0.9)
dist_eps_list=c("stdN")
d=4+1
burn_in=200

simulation1 = data.frame("Distribution_Eps"=character(0), "Method"=character(0),
                         "p"=numeric(), 
                         "beta1_MCSE"=numeric(),
                         "beta2_MCSE"=numeric(), 
                         "beta3_MCSE"=numeric(), 
                         "beta4_MCSE"=numeric(), 
                         "beta5_MCSE"=numeric(), stringsAsFactors=F)

```

## NMES1988 Dataset
The data was sourced from US National Medical Expenditure Survey [NMES] data for 1987/88. Available as NMES1988 in package AER (Kleiber and Zeileis 2008). Originally taken from Deb and Trivedi (J. Applied Econometrics 1997)
```{r}
head(NMES1988)
```

## Model: visits ~ chronic+age+school+income

## Quantreg
```{r}
rqfit <- rq(visits ~ chronic+age+school+income, data = NMES1988, tau = quantiles)
summary(rqfit)
```

\newpage

## Beta_p estimations vs rq() coefficients

The plot titles are formatted as (sampling method)_(quantile)_(error distribution)_(beta_p). The histograms are the beta_p estimations yielded by the paper's model. The red horizontal line reflects rq() beta coefficients. The absence of red lines in some plots reflects big difference in our beta_p estimations and the rq() results.

## Notations:
GWS: Gibbs sampler of the asymmetric Laplace distribution (ALD) with Scale parameter\newline
GWOS: Gibbs sampler of the asymmetric Laplace distribution (ALD) without Scale parameter\newline
stdN: Standard Normal Prior\newline
beta_1: Intercept\newline
beta_2: Regression coefficient associated with chronic\newline
beta_3: Regression coefficient associated with age\newline
beta_4: Regression coefficient associated with school\newline
beta_5: Regression coefficient associated with income


## Histograms
```{r,fig.height=3.5, fig.width=8， warning=FALSE, echo=FALSE}
par(mfrow=c(1,5))
# setwd('C:\\Users\\juyil\\Dropbox\\Study\\GitHub\\Bayesian-gibbs-sampler\\R')
for (p in quantiles){
    rqfit = rq(mpg ~ cyl+drat+vs, data = mtcars, tau = p)
    for (dist_eps in dist_eps_list){
        load(paste0("NMES\\Gibbs with Scale\\","GWS_",p,"_",dist_eps,"_betap.RData"))
        beta_p = list()
        for (i in 1:d){
          beta_p[[i]]=unlist(lapply(beta_p_record, function(x){return(x[i,])}))[(burn_in+1):itr_total]
          hist(beta_p[[i]], main=paste("GWS_",p,"_",dist_eps,"\n_beta_",i), xlab=paste("beta",i),
               xlim=c(min(min(beta_p[[i]]),summary(rqfit)$coefficients[i]),max(max(beta_p[[i]]),summary(rqfit)$coefficients[i])))
          abline(v=summary(rqfit)$coefficients[i],col="red",lwd=3)
        }
        new_obs = list(dist_eps, "GWS", as.numeric(p), 
                    as.numeric(mcse(beta_p[[1]])$se), as.numeric(length(beta_p[[1]])/effectiveSize(beta_p[[1]])), 
                    as.numeric(mean(beta_p[[1]])), as.numeric(sd(beta_p[[1]])),
                    as.numeric(beta_p[[1]][length(beta_p[[1]])]),
                    as.numeric(mcse(beta_p[[2]])$se), as.numeric(length(beta_p[[2]])/effectiveSize(beta_p[[2]])),
                    as.numeric(mean(beta_p[[2]])), as.numeric(sd(beta_p[[2]])),
                    as.numeric(beta_p[[2]][length(beta_p[[2]])]),
                    as.numeric(mcse(beta_p[[3]])$se), as.numeric(length(beta_p[[3]])/effectiveSize(beta_p[[3]])), 
                    as.numeric(mean(beta_p[[3]])), as.numeric(sd(beta_p[[3]])),
                    as.numeric(beta_p[[3]][length(beta_p[[3]])]),
                    as.numeric(mcse(beta_p[[4]])$se), as.numeric(length(beta_p[[4]])/effectiveSize(beta_p[[4]])), 
                    as.numeric(mean(beta_p[[4]])), as.numeric(sd(beta_p[[4]])),
                    as.numeric(beta_p[[4]][length(beta_p[[4]])]),
                    as.numeric(mcse(beta_p[[5]])$se), as.numeric(length(beta_p[[5]])/effectiveSize(beta_p[[5]])), 
                    as.numeric(mean(beta_p[[5]])), as.numeric(sd(beta_p[[5]])),
                    as.numeric(beta_p[[5]][length(beta_p[[5]])]))
        simulation1[nrow(simulation1)+1,] = new_obs
        
################################################################   
        load(paste0("NMES\\Gibbs without Scale\\","GWOS_",p,"_",dist_eps,"_betap.RData"))
        beta_p = list()
        for (i in 1:d){
          beta_p[[i]]=unlist(lapply(beta_p_record, function(x){return(x[i,])}))[(burn_in+1):itr_total]
          hist(beta_p[[i]],  main=paste("GWOS_",p,"_",dist_eps,"\n_beta_",i), xlab=paste("beta",i),
               xlim=c(min(min(beta_p[[i]]),summary(rqfit)$coefficients[i]),max(max(beta_p[[i]]),summary(rqfit)$coefficients[i])))
          abline(v=summary(rqfit)$coefficients[i],col="red",lwd=3)
        }
        new_obs = list(dist_eps, "GWOS", as.numeric(p), 
                    as.numeric(mcse(beta_p[[1]])$se), as.numeric(length(beta_p[[1]])/effectiveSize(beta_p[[1]])), 
                    as.numeric(mean(beta_p[[1]])), as.numeric(sd(beta_p[[1]])),
                    as.numeric(beta_p[[1]][length(beta_p[[1]])]),
                    as.numeric(mcse(beta_p[[2]])$se), as.numeric(length(beta_p[[2]])/effectiveSize(beta_p[[2]])),
                    as.numeric(mean(beta_p[[2]])), as.numeric(sd(beta_p[[2]])),
                    as.numeric(beta_p[[2]][length(beta_p[[2]])]),
                    as.numeric(mcse(beta_p[[3]])$se), as.numeric(length(beta_p[[3]])/effectiveSize(beta_p[[3]])), 
                    as.numeric(mean(beta_p[[3]])), as.numeric(sd(beta_p[[3]])),
                    as.numeric(beta_p[[3]][length(beta_p[[3]])]),
                    as.numeric(mcse(beta_p[[4]])$se), as.numeric(length(beta_p[[4]])/effectiveSize(beta_p[[4]])), 
                    as.numeric(mean(beta_p[[4]])), as.numeric(sd(beta_p[[4]])),
                    as.numeric(beta_p[[4]][length(beta_p[[4]])]),
                    as.numeric(mcse(beta_p[[5]])$se), as.numeric(length(beta_p[[5]])/effectiveSize(beta_p[[5]])), 
                    as.numeric(mean(beta_p[[5]])), as.numeric(sd(beta_p[[5]])),
                    as.numeric(beta_p[[5]][length(beta_p[[5]])]))
        simulation1[nrow(simulation1)+1,] = new_obs
    }
}

```


## Traceplots

```{r,fig.height=3.5, fig.width=8， warning=FALSE, echo=FALSE}
par(mfrow=c(1,5))
# setwd('C:\\Users\\juyil\\Dropbox\\Study\\GitHub\\Bayesian-gibbs-sampler\\R')
for (p in quantiles){
    rqfit = rq(mpg ~ cyl+drat+vs, data = mtcars, tau = p)
    for (dist_eps in dist_eps_list){
        load(paste0("NMES\\Gibbs with Scale\\","GWS_",p,"_",dist_eps,"_betap.RData"))
        beta_p = list()
        for (i in 1:d){
          beta_p[[i]]=unlist(lapply(beta_p_record, function(x){return(x[i,])}))[(burn_in+1):itr_total]
          plot(beta_p[[i]],type="l", main=paste("GWS_",p,"_",dist_eps,"\n_beta_",i), xlab=paste("beta",i),
               ylim=c(min(min(beta_p[[i]]),summary(rqfit)$coefficients[i]),max(max(beta_p[[i]]),summary(rqfit)$coefficients[i])))
          abline(h=summary(rqfit)$coefficients[i],col="red",lwd=3)
        }
        new_obs = list(dist_eps, "GWS", as.numeric(p), 
                    as.numeric(mcse(beta_p[[1]])$se), as.numeric(length(beta_p[[1]])/effectiveSize(beta_p[[1]])), 
                    as.numeric(mean(beta_p[[1]])), as.numeric(sd(beta_p[[1]])),
                    as.numeric(beta_p[[1]][length(beta_p[[1]])]),
                    as.numeric(mcse(beta_p[[2]])$se), as.numeric(length(beta_p[[2]])/effectiveSize(beta_p[[2]])),
                    as.numeric(mean(beta_p[[2]])), as.numeric(sd(beta_p[[2]])),
                    as.numeric(beta_p[[2]][length(beta_p[[2]])]),
                    as.numeric(mcse(beta_p[[3]])$se), as.numeric(length(beta_p[[3]])/effectiveSize(beta_p[[3]])), 
                    as.numeric(mean(beta_p[[3]])), as.numeric(sd(beta_p[[3]])),
                    as.numeric(beta_p[[3]][length(beta_p[[3]])]),
                    as.numeric(mcse(beta_p[[4]])$se), as.numeric(length(beta_p[[4]])/effectiveSize(beta_p[[4]])), 
                    as.numeric(mean(beta_p[[4]])), as.numeric(sd(beta_p[[4]])),
                    as.numeric(beta_p[[4]][length(beta_p[[4]])]),
                    as.numeric(mcse(beta_p[[5]])$se), as.numeric(length(beta_p[[5]])/effectiveSize(beta_p[[5]])), 
                    as.numeric(mean(beta_p[[5]])), as.numeric(sd(beta_p[[5]])),
                    as.numeric(beta_p[[5]][length(beta_p[[5]])]))
        simulation1[nrow(simulation1)+1,] = new_obs
        
################################################################   
        load(paste0("NMES\\Gibbs without Scale\\","GWOS_",p,"_",dist_eps,"_betap.RData"))
        beta_p = list()
        for (i in 1:d){
          beta_p[[i]]=unlist(lapply(beta_p_record, function(x){return(x[i,])}))[(burn_in+1):itr_total]
          plot(beta_p[[i]],type="l",  main=paste("GWOS_",p,"_",dist_eps,"\n_beta_",i), xlab=paste("beta",i),
               ylim=c(min(min(beta_p[[i]]),summary(rqfit)$coefficients[i]),max(max(beta_p[[i]]),summary(rqfit)$coefficients[i])))
          abline(h=summary(rqfit)$coefficients[i],col="red",lwd=3)
        }
        new_obs = list(dist_eps, "GWOS", as.numeric(p), 
                    as.numeric(mcse(beta_p[[1]])$se), as.numeric(length(beta_p[[1]])/effectiveSize(beta_p[[1]])), 
                    as.numeric(mean(beta_p[[1]])), as.numeric(sd(beta_p[[1]])),
                    as.numeric(beta_p[[1]][length(beta_p[[1]])]),
                    as.numeric(mcse(beta_p[[2]])$se), as.numeric(length(beta_p[[2]])/effectiveSize(beta_p[[2]])),
                    as.numeric(mean(beta_p[[2]])), as.numeric(sd(beta_p[[2]])),
                    as.numeric(beta_p[[2]][length(beta_p[[2]])]),
                    as.numeric(mcse(beta_p[[3]])$se), as.numeric(length(beta_p[[3]])/effectiveSize(beta_p[[3]])), 
                    as.numeric(mean(beta_p[[3]])), as.numeric(sd(beta_p[[3]])),
                    as.numeric(beta_p[[3]][length(beta_p[[3]])]),
                    as.numeric(mcse(beta_p[[4]])$se), as.numeric(length(beta_p[[4]])/effectiveSize(beta_p[[4]])), 
                    as.numeric(mean(beta_p[[4]])), as.numeric(sd(beta_p[[4]])),
                    as.numeric(beta_p[[4]][length(beta_p[[4]])]),
                    as.numeric(mcse(beta_p[[5]])$se), as.numeric(length(beta_p[[5]])/effectiveSize(beta_p[[5]])), 
                    as.numeric(mean(beta_p[[5]])), as.numeric(sd(beta_p[[5]])),
                    as.numeric(beta_p[[5]][length(beta_p[[5]])]))
        simulation1[nrow(simulation1)+1,] = new_obs
    }
}

```

```{r,include=FALSE}
# ord = c("stdN","heteroN","student")
# simulation1$Distribution_Eps = factor(simulation1$Distribution_Eps,levels=ord)
# simulation1 = simulation1[order(simulation1$Distribution_Eps),]
# is.num <- sapply(simulation1, is.numeric)
# simulation1[is.num] <- lapply(simulation1[is.num], round, 4)
# simulation1

```

